Limit Theory for Out-of-Sample Comparisons of Overfit Models

### 2012-03-30 mc/plot-insample-size.Rnw
Collapsed hold history into a single commit

<<fig=TRUE,width=5.5, height=4>>=
library(fwPackage)
library(lattice)
ltheme <- canonical.theme(color = FALSE)     ## in-built B&W theme  
ltheme$strip.background$col <- "transparent" ## change strip bg  
lattice.options(default.theme = ltheme)      ## set as default

dbc <- dbConnect(dbDriver("SQLite"), dbname = "simulations.db")
d <- dbGetQuery(dbc, "select reject, 'T=' || n as nlabel, altlabel, norm from viewftest 
                                     where label='size' and norm in (0,1)")
d$norm <- as.factor(d$norm)

print(dotplot(norm ~ reject | interaction(altlabel,nlabel, sep = ", "),
              dat = d, las = 1,
              xlab = "Rejection Probability", ylab = "c",
              xlim = c(-.1, 1.1),
              panel = function(x, y, ...) {
                panel.dotplot(x, y, ..., type = "n")
                panel.text(x, as.numeric(y), labels = sprintf("%.2f", x))
              },
              par.strip.text = list(cex = .65),
              layout = c(2,4),
              index.cond = list(c(3,4,7,8,5,6,1,2))))
@

>>>>

<<fig=TRUE>>=
library(fwPackage)
library(lattice)

dbc <- dbConnect(dbDriver("SQLite"), dbname = "simulations.db")

print(dotplot(norm ~ reject | interaction(altlabel,nlabel, sep = ", "),
              dat = dbGetQuery(dbc, "select reject, 'n=' || n as nlabel, altlabel, norm from viewftest 
                                     where label='size' and norm in (0,1)"),
              xlab = "Rejection Probability",
              xlim = c(-.1, 1.1),
              panel = function(x, y, ...) {
                panel.dotplot(x, y, ..., type = "n")
                panel.text(x, as.numeric(y), labels = sprintf("%.2f", x))
              },
              par.settings = standard.theme(color=FALSE),
              par.strip.text = list(cex = .65),
              layout = c(2,4),
              index.cond = list(c(3,4,7,8,5,6,1,2)),
              main = "Rejection probability for F-test at 10% (size)\nbenchmark has smaller generalization error"))
@

### 2012-03-30 mc/plot-interval.Rnw
Collapsed hold history into a single commit

<<>>=
library(fwPackage)
library(lattice)
ltheme <- canonical.theme(color = FALSE)     ## in-built B&W theme  
ltheme$strip.background$col <- "transparent" ## change strip bg  
lattice.options(default.theme = ltheme)      ## set as default

dbc <- dbConnect(dbDriver("SQLite"), dbname = "simulations.db")
mcpars <- dbGetQuery(dbc, "select count(jobnumber) as njobs from interval")
dstring <- "
select * from (select ntest, isim, idgp, transform, label, avg(reject) as reject
from interval 
where label='%s' and simIndex <= %d and transform = 'difference'
group by ntest, isim, idgp, transform, label) s 
join nobs n join coefficients c on n.i=s.isim and c.i=s.idgp"

doxyplot <- function(dplot, ...) {
  print(xyplot(I(1 - reject) ~ I(ntest/n) | interaction(nlabel, altlabel, normlabel, sep = ", "),
               data = dplot,
               ylab = "Coverage", xlab = "P/T",
               panel = function(x,y,...) {
                 panel.xyplot(x,y,...,type = "l")
                 panel.lines(c(0,2/3),c(.9,.9), col = "gray")
               },
               layout = c(4,4),
               par.strip.text = list(cex = .65),
               index.cond = list(c(13,15,16,14,9,11,12,10,5,7,8,6,1,3,4,2))))
}
@

<<testerror1, fig=TRUE, height = 3.5, width=6>>=
d <- dbGetQuery(dbc, sprintf(dstring, 'test.error.1', 500))
d$nlabel <- sprintf("T=%d", d$n)
d$normlabel <- sprintf("c=%d", d$norm)

doxyplot(d) #Empirical coverage of one-sided interval
@

<<testerror2, fig=TRUE, height = 3.5, width=6>>=
d <- dbGetQuery(dbc, sprintf(dstring, 'test.error.2', 500))
d$nlabel <- sprintf("T=%d", d$n)
d$normlabel <- sprintf("c=%d", d$norm)
doxyplot(d) #Empirical coverage of two-sided interval
@

<<generror1, fig=TRUE, height = 3.5, width=6>>=
d <- dbGetQuery(dbc, sprintf(dstring, 'gen.error.1', 500))
d$nlabel <- sprintf("T=%d", d$n)
d$normlabel <- sprintf("c=%d", d$norm)
doxyplot(d) #Empirical coverage of one-sided interval
@

<<generror2, fig=TRUE, height = 3.5, width=6>>=
d <- dbGetQuery(dbc, sprintf(dstring, 'gen.error.2', 500))
d$nlabel <- sprintf("T=%d", d$n)
d$normlabel <- sprintf("c=%d", d$norm)
doxyplot(d) #Empirical coverage of two-sided interval
@

<<>>=
dbDisconnect(dbc)
@
\end{document}

>>>>

<<>>=
library(fwPackage)
library(lattice)

dbc <- dbConnect(dbDriver("SQLite"), dbname = "simulations.db")
d <- dbGetQuery(dbc, "
select * from (select ntest, isim, idgp, transform, label, avg(reject) as reject
from interval 
where label in ('test.error.1', 'test.error.2', 'gen.error.1', 'gen.error.2')
and simIndex <= 500
group by ntest, isim, idgp, transform, label) s 
join nobs n join coefficients c on n.i=s.isim and c.i=s.idgp")
d$nlabel <- sprintf("n=%d", d$n)
d$normlabel <- sprintf("c=%d", d$norm)

doxyplot <- function(dframe, label, maintext, ...) {
  dplot <- dframe[dframe$label==label,]
  print(xyplot(I(1 - reject) ~ ntest | interaction(nlabel, altlabel, normlabel, sep = ", "),
               data = dplot,
               ylab = "coverage", main = maintext,
##               ylim = c(-0.05,1.05),
               panel = function(x,y,...) {
                 panel.xyplot(x,y,...,type = "l")
                 panel.lines(c(1,600),c(.9,.9), col = rgb(0,0,0,0.5))
               },
               par.strip.text = list(cex = .65),
               index.cond = list(c(13,15,16,14,9,11,12,10,5,7,8,6,1,3,4,2)),
               par.settings = standard.theme(color=FALSE),...))
}
@

<<fig=TRUE>>=
doxyplot(d, "test.error.1", "Empirical coverage of one-sided interval")
@

<<fig=TRUE>>=
doxyplot(d, "test.error.2", "Empirical coverage of two-sided interval")
@

<<fig=TRUE>>=
doxyplot(d, "gen.error.1", "Empirical coverage of one-sided interval")
@

<<fig=TRUE>>=
doxyplot(d, "gen.error.2", "Empirical coverage of two-sided interval")
@

<<fig=TRUE>>=
doxyplot(d, "gen.error.2", "Details of empirical coverage of two-sided interval", 
         xlim = c(0,350), ylim = c(.75, .95))
@ 
<<>>=
dbDisconnect(dbc)
@
\end{document}

### 2012-03-30 mc/plot-oos-size.Rnw
Collapsed hold history into a single commit

<<>>=
library(fwPackage)
library(lattice)
ltheme <- canonical.theme(color = FALSE)     ## in-built B&W theme  
ltheme$strip.background$col <- "transparent" ## change strip bg  
lattice.options(default.theme = ltheme)      ## set as default

@@

d <- dbGetQuery(dbc, "
select * from (select ntest, isim, idgp, transform, label, avg(reject) as reject
from interval 
where label='size' and idgp in (1,2) and transform in ('mccracken', 'clarkwest', 'difference')
group by ntest, isim, idgp, transform, label) s 
join nobs n join coefficients c on n.i=s.isim and c.i=s.idgp")
d$nlabel <- sprintf("T=%d", d$n)
d$normlabel <- sprintf("c=%d", d$norm)

dpower <- dbGetQuery(dbc, "
select * from (select ntest, isim, idgp, transform, label, avg(reject) as reject
from interval 
where label='power' and idgp in (2,3) and transform='difference'
group by ntest, isim, idgp, transform, label) s 
join nobs n join coefficients c on n.i=s.isim and c.i=s.idgp")
dpower$nlabel <- sprintf("T=%d", dpower$n)
dpower$normlabel <- sprintf("c=%d", dpower$norm)

@@

doxyplot <- function(dframe, ...) {
  print(xyplot(reject ~ I(ntest/n) | interaction(nlabel,altlabel,normlabel, sep = ", "),
               data = dframe,
               ylab = "Rejection Probability", xlab = "P/T",
               panel = function(x,y,...) {
                 panel.lines(c(0,2/3),c(.1,.1), col = "lightgray")
                 panel.xyplot(x,y,...,type = "l")
               },
               layout = c(4,4),
               par.strip.text = list(cex = .65),
               index.cond = list(c(13,15,16,14,9,11,12,10,5,7,8,6,1,3,4,2))))
}
@

Empirical size of Clark and West test at 90\% confidence
<<clarkwest, fig=TRUE, width=6>>=
doxyplot(d[d$transform == "clarkwest",])
@

Empirical size of McCracken test at 90\% confidence
<<mccracken, fig=TRUE, width=6, height=3.5>>=
  print(xyplot(reject ~ I(ntest/n) | interaction(nlabel,altlabel,normlabel, sep = ", "),
               data = d[d$altlabel=="K=3" & d$transform == "mccracken",],
               ylab = "Rejection Probability", xlab = "P/T",
               panel = function(x,y,...) {
                 panel.lines(c(0,2/3),c(.1,.1), col = "lightgray")
                 panel.xyplot(x,y,...,type = "l")
               },
               layout = c(4,2),
               par.strip.text = list(cex = .65),
               index.cond = list(c(5,7,8,6,1,3,4,2))))
## doxyplot(d[d$altlabel=="K=3" & d$transform == "mccracken",])         
@

Empirical size of Naive OOS test at 90\% confidence
<<dmwsize, fig=TRUE, width=6>>=
doxyplot(d[d$transform == "difference",])
@

Empirical power of Naive oos test at 90\% confidence
<<dmwpower, fig=TRUE, width=6>>=
doxyplot(dpower[dpower$transform == "difference",]) 
@

>>>>

<<>>=
library(fwPackage)
library(lattice)

@@

d <- dbGetQuery(dbc, "
select * from (select ntest, isim, idgp, transform, label, avg(reject) as reject
from interval 
where label='size' and idgp in (1,2) and transform in ('mccracken', 'clarkwest', 'difference')
group by ntest, isim, idgp, transform, label) s 
join nobs n join coefficients c on n.i=s.isim and c.i=s.idgp")
d$nlabel <- sprintf("n=%d", d$n)
d$normlabel <- sprintf("c=%d", d$norm)

dpower <- dbGetQuery(dbc, "
select * from (select ntest, isim, idgp, transform, label, avg(reject) as reject
from interval 
where label='power' and idgp in (2,3) and transform='difference'
group by ntest, isim, idgp, transform, label) s 
join nobs n join coefficients c on n.i=s.isim and c.i=s.idgp")
dpower$nlabel <- sprintf("n=%d", dpower$n)
dpower$normlabel <- sprintf("c=%d", dpower$norm)

@@

doxyplot <- function(dframe, maintext, ...) {
  print(xyplot(reject ~ ntest | interaction(nlabel,altlabel,normlabel, sep = ", "),
               data = dframe,
               ylab = "size", main = maintext,
               panel = function(x,y,...) {
                 panel.xyplot(x,y,...,type = "l")
                 panel.lines(c(1,600),c(.1,.1), col = rgb(0,0,0,0.5))
               },
               layout = c(4,4),
               par.strip.text = list(cex = .65),
               index.cond = list(c(13,15,16,14,9,11,12,10,5,7,8,6,1,3,4,2)),
               par.settings = standard.theme(color=FALSE)))
}
@

<<fig=TRUE>>=
doxyplot(d[d$transform == "clarkwest",], 
         "Empirical size of Clark and West test at 90% confidence")
@

<<fig=TRUE>>=
doxyplot(d[d$altlabel=="K=3" & d$transform == "mccracken",], 
         "K=3", "Empirical size of McCracken test at 90% confidence")
@

<<fig=TRUE>>=
doxyplot(d[d$transform == "difference",], 
         "K=3", "Empirical size of Naive OOS test at 90% confidence", auto.key = list(lines=TRUE, points=FALSE))
@

<<fig=TRUE>>=
doxyplot(dpower[dpower$transform == "difference",], 
         "Empirical power of Naive oos test at 90% confidence", auto.key = list(lines=TRUE, points=FALSE))
@
